Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2013-07-02 inst/doc/nonparametric-bayes.Rmd

[@Fischer2009, @Polasky2011]

Decision making under uncertainty is a ubiquitous challenge of natural 
resource management and conservation.  
Here we illustrate how a stochastic dynamic programming algorithm can 
be driven by the predictions from a Gaussian process model, sidestepping
the need for an accurate model-based description of the sustem dynamics.

@@

[@Reed1979, @Mangel1985]

>>>>

Decision making under uncertainty is a ubiquitous challenge of natural 
resource management and conservation.  
Here we illustrate how a stochastic dynamic programming algorithm can 
be driven by the predictions from a Gaussian process model, sidestepping
the need for an accurate model-based description of the system dynamics.

add references to [@Fischer2009, @Polasky2011] as persective on combining complex / critical dynamics + control theory

@@

More historical context, e.g. [@Reed1979, @Mangel1985]
